High-Order Accurate Finite Difference Schemes \\ for Variable-Coefficient PDEs via Optimal Time Step Selection

### 2008-08-10 papers/OTSPDE-VarCoefs/OTSPDE-VarCoefs.tex
OTSPDE: * Checked in place holders for upcoming papers. * Updated information on potential journals to submit to.

\title{High-Order Accurate Finite Difference Schemes \\
       for Systems of PDEs via Optimal Time Step Selection}

\author{
Kevin T. Chu\footnotemark[2] \footnotemark[3]
}

@@

@@

\begin{abstract}
place holder...
\end{abstract}

\begin{keywords}
optimal time step, finite difference schemes, high-order accurate numerical 
methods, time dependent PDEs, systems of PDEs
\end{keywords}

\begin{AMS}
65-02, 65M06, 65M12, 65M20, ??
\end{AMS}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{KEVIN T. CHU}
         {HIGH-ORDER FD SCHEMES VIA OPTIMAL TIME STEPS}

\section*{Introduction}
High-order numerical methods for partial differential equations (PDEs) will 
always be valuable for increasing the computational efficiency of numerical 
simulations.  Thus, it is not at all surprising that a great deal of effort in 
numerical PDEs continues to be focused on the development of high-order 
numerical schemes~\cite{bruger_2005, gibou_2005, ito_2005, shukla_2005, 
shukla_2007}.  
Typically, high-order accuracy is achieved by constructing
schemes that have high formal orders of accuracy.  However, high-order 
accurate numerical solutions can also be obtained by using formally low-order 
schemes in clever ways.  When possible, the latter approach can be a powerful 
way to boost the accuracy of a numerical method \emph{without} introducing too 
much additional algorithmic (and programming) complexity.

\section{\label{sec:summary} Summary}

\section*{Acknowledgments}
The author gratefully acknowledges the support of Vitamin D, Inc.
and the Institute for High-Performance Computing (IHPC) in Singapore. 
The author would like to thank K.-H. Chiam, ?? 
for helpful suggestions on the manuscript.  
The author particularly thanks K.-H. Chiam for pointing him to the 
mathematical biology literature for interesting examples of reaction-diffusion 
systems.

\bibliography{OTSPDE-Systems}

>>>>

\title{High-Order Accurate Finite Difference Schemes \\
       for Variable-Coefficient PDEs via Optimal Time Step Selection}

\author{
Kevin T. Chu\footnotemark[2] \footnotemark[3]
and 
James V. Lambers\footnotemark[4]
}

@@

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[4]{Department of Energy Resources Engineering, Stanford University, Stanford, CA 94305}

@@

\begin{abstract}
place holder
\end{abstract}

\begin{keywords}
optimal time step, finite difference schemes, high-order accurate numerical 
methods, time dependent PDEs, variable-coefficient PDEs
\end{keywords}

\begin{AMS}
65-02, 65M06, 65M12, 65M20 ??
\end{AMS}

\pagestyle{myheadings}
\thispagestyle{plain}
\markboth{KEVIN T. CHU AND JAMES V. LAMBERS}
         {??}

\section*{Introduction}
\cite{zoppou1999, kreiss2002, guidotti2006}

% ACKNOWLEDGMENTS
\section*{Acknowledgments}
The author gratefully acknowledges the support of Vitamin D, Inc.
and the Institute for High-Performance Computing (IHPC) in Singapore. 
The author would like to thank ??
for helpful suggestions on the manuscript.

\bibliography{OTSPDE-VarCoefs}
